|

### 2021-03-14 documentation/paper.Rmd
Remove references to "PollBasePro"

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(PollBasePro::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, Y, and Z. We would also like to extend a special thanks to all of the volunteers who have given their time to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("PollBasePro"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(PollBasePro::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

library(PollBasePro)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(tidybayes)
library(patchwork)
library(brms)
library(here)

@@

death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("PollBasePro"), ".rds")))

@@

cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("PollBasePro"), ".rds")))
cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("PollBasePro"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("PollBasePro"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("PollBasePro"), ".rds")))

@@

In this paper, we introduce PollBasePro: the most comprehensive time series of British voting intention data assembled to date. The dataset contains `r format(nrow(PollBasePro::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. Furthermore, our data are well validated and follow the course of British political history. We therefore expect PollBasePro to become a valuable resource for students of British politics in the years to come.

>>>>

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(BritPol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, Y, and Z. We would also like to extend a special thanks to all of the volunteers who have given their time to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("BritPol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(BritPol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

library(BritPol)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(tidybayes)
library(patchwork)
library(brms)
library(here)

@@

death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("BritPol"), ".rds")))

@@

cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("BritPol"), ".rds")))
cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("BritPol"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("BritPol"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))

@@

In this paper, we introduce PollBasePro: the most comprehensive time series of British voting intention data assembled to date. The dataset contains `r format(nrow(BritPol::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. Furthermore, our data are well validated and follow the course of British political history. We therefore expect PollBasePro to become a valuable resource for students of British politics in the years to come.

### 2021-03-14 documentation/readme.Rmd
Remove references to "PollBasePro"

library(PollBasePro)
library(tidyverse)
library(lubridate)
library(here)

@@

# PollBasePro

PollBasePro is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. The user guide and codebook is available [here](https://github.com/jackobailey/PollBasePro/blob/master/download/userguide.pdf) and the accompanying paper is available [here](https://github.com/jackobailey/PollBasePro/blob/master/download/paper.pdf).

To install the latest version of PollBasePro, run the following code in `R`:

``` r
devtools::install_github("jackobailey/PollBasePro")
```

We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users. These files include all necessary value and variable labels and should work seamlessly with both software packages. [Click here to download them](https://github.com/jackobailey/PollBasePro/tree/master/download).

@@

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  jbmisc::theme_bailey() +
  labs(
    title = paste0("British Poll of Polls, ", str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")),
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Based on data from PollBasePro, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/PollBasePro"
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )

@@

<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png"></center>

@@

Both `pollbase` and `pollbasepro` are living datasets. As such, users should try to use only the most recent version of the data when conducting their analyses. Like any project of this size, we cannot rule out the possibility that minor mistakes might have crept into our data processing pipeline. If you think that you have found an error in our code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/PollBasePro/issues) or [contact us directly](mailto:jack.bailey@manchester.ac.uk).

We are happy for others to use our code for their own purposes, but ask that they do so *with attribution*. That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you based your analysis on our work. The citations for each item in PollBasePro are as follows:

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("PollBasePro")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from https://doi.org/10.7910/DVN/3POIQW.

- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("PollBasePro")`: User Guide and Codebook. Retrieved from doi.

>>>>

library(BritPol)
library(tidyverse)
library(lubridate)
library(here)

@@

# BritPol

BritPol is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. A user guide and codebook is available for `pollbasepro` [here](https://github.com/jackobailey/BritPol/blob/master/download/userguide.pdf) and an accompanying paper is available [here](https://github.com/jackobailey/BritPol/blob/master/download/paper.pdf).

To install the latest version of BritPol, run the following code in `R`:

``` r
devtools::install_github("jackobailey/BritPol")
```

We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users. These files include all necessary value and variable labels and should work seamlessly with both software packages. [Click here to download them](https://github.com/jackobailey/BritPol/tree/master/download).

@@

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  theme_minimal() +
    theme(
      legend.position = "bottom",
      legend.title = element_blank(),
      text = element_text(family = "Cabin", color = "black", size = 8),
      plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
      plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
      axis.line = element_line(lineend = "round"),
      axis.title.x = element_blank(),
      axis.text.x = element_text(color = "black", size = rel(1)),
      axis.ticks.x = element_line(lineend = "round"),
      axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
      axis.text.y = element_text(color = "black", size = rel(1)),
      strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
      panel.spacing = unit(.3, "cm"),
      panel.grid.major.y = element_line(size = .5, lineend = "round"),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    ) +
  labs(
    title = paste0("British Poll of Polls, ", str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")),
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Based on data from BritPol, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/BritPol"
  )

@@

<center><img src="https://raw.githubusercontent.com/jackobailey/BritPol/master/documentation/_assets/timeplot_gh.png"></center>

@@

Both `pollbase` and `pollbasepro` are living datasets. As such, users should try to use only the most recent version of the data when conducting their analyses. Like any project of this size, we cannot rule out the possibility that minor mistakes might have crept into our data processing pipeline. If you think that you have found an error in our code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/BritPol/issues) or [contact us directly](mailto:jack.bailey@manchester.ac.uk).

We are happy for others to use our code for their own purposes, but ask that they do so *with attribution*. That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you based your analysis on our work. The citations for each item in BritPol are as follows:

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("BritPol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from https://doi.org/10.7910/DVN/3POIQW.

- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("BritPol")`: User Guide and Codebook. Retrieved from doi.

### 2021-03-14 documentation/userguide.Rmd
Remove references to "PollBasePro"

---
title: |
  | PollBasePro v`r packageVersion("PollBasePro")` (Beta)
  | User Guide and Codebook
date: |
  | This version: `r stringr::str_remove(format(Sys.time(), "%d %B %Y"), "^0")`
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/cb-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("PollBasePro"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("PollBasePro"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("PollBasePro"), ".rds")))

@@

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("PollBasePro")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from https://doi.org/10.7910/DVN/3POIQW.

- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("PollBasePro")`: User Guide and Codebook. Retrieved from doi.

@@

- ``r paste0("pollbase_", packageVersion("PollBasePro"), ".dta")``
- ``r paste0("pollbasepro_", packageVersion("PollBasePro"), ".dta")``
- ``r paste0("pollbase_", packageVersion("PollBasePro"), ".sav")``
- ``r paste0("pollbasepro_", packageVersion("PollBasePro"), ".sav")``

>>>>

---
title: |
  | PollBasePro v`r packageVersion("BritPol")` (Beta)
  | User Guide and Codebook
date: |
  | This version: `r stringr::str_remove(format(Sys.time(), "%d %B %Y"), "^0")`
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/cb-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("BritPol"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("BritPol"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))

@@

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("BritPol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from https://doi.org/10.7910/DVN/3POIQW.

- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("BritPol")`: User Guide and Codebook. Retrieved from doi.

@@

- ``r paste0("pollbase_", packageVersion("BritPol"), ".dta")``
- ``r paste0("pollbasepro_", packageVersion("BritPol"), ".dta")``
- ``r paste0("pollbase_", packageVersion("BritPol"), ".sav")``
- ``r paste0("pollbasepro_", packageVersion("BritPol"), ".sav")``
